GPU-friendly Stroke Expansion

### 2024-04-29 paper.tex

We measured the timing of our CPU implementation, generating both line and arc primitives, against Skia's stroker, which outputs a mix of straight lines and quadratic Bézier primitives. The results are shown in Figure~\ref{fig:timings}. The time shown is the total for test files from the \emph{timings} dataset of \citet{Nehab2020}, and the tolerance in all cases was 0.25. TODO: measure against other implementations.

>>>>

We measured the timing of our CPU implementation, generating both line and arc primitives, against the Nehab and Skia strokers, which both output a mix of straight lines and quadratic Bézier primitives. The results are shown in Figure~\ref{fig:timings}. The time shown is the total for test files from the \emph{timings} dataset of \citet{Nehab2020}, and the tolerance was 0.25 when adjustable as a parameter.
